---
title: "PSY 8712 Week 8 Project"
author: "Kyrene"
date: "2026-03-22"
output: 
   html_document:
     theme:
        bootswatch: cosmo
        fg: "#0000FF"
        bg: "#FFFFFF"
     toc: true
     toc_float: true
     df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link]. https://mybinder.org/v2/gh/Kyrene0629/psy8712-week8.git/HEAD.
An interactive web app is available by [clicking this link instead]. https://kyrene0629.shinyapps.io/shiny_week8/.

**Script Settings and Resources**
```{r Script Settings and Resources, echo = T, warning = F, message = F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(kableExtra)
```

**Data Import and Cleaning**
I imported and cleaned the data like how i did last week. Also, I realize the class for qs are already integer, i should double check before i write that. I reverse-coded q5 by just using 6 - q5 because it is on 1-5 likert scale, then 1 -> 5, 2 -> 4, 3 -> 3, 4 -> 2, 5 -> 1. Lastly, I create two variables called mean_q1q6 and mean_q8q10 by calculate the mean for q1-q6 on x axis and q8 to q10 on y axis to prepare for following questions.
```{r data import and cleaning}
week8_tbl <- read.csv("../data/week3.csv") %>%
  mutate(
    timeStart = ymd_hms(timeStart),
    condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control")),
    gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
    q5 = 6 - q5,
    mean_q1q6 = rowMeans(across(q1:q6)),
    mean_q8q10 = rowMeans(across(q8:q10)))
```

**Visualization**
I used kable() to visually display the data in week8_tbl contained q1 to q6 based on the question. I used what i got from last code chunk (mean scores for q1 to q6 and mean scores for q8 to q10) and pass this into ggplot() and map mean_q1q6 to x axis and mean_q8q10 to y axis. I then put geom_point() to put one point for each person on the scatterplot. I add a purple OLS regression line and the shaded error band. Lastly, i label the x axis and y axis accordingly.
```{r Visualization, echo = F, warning = F, message = F}
week8_tbl %>%
  select(q1:q6) %>%
  kable()

week8_tbl %>%
  ggplot(aes(x = mean_q1q6, y = mean_q8q10)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, color = "purple") +
  scale_x_continuous(name = "Mean Scores on Q1-Q6") +
  scale_y_continuous(name = "Mean Scores on Q8-Q10")
```

**Analysis**
I did a Pearson correlation test between these two means and save that to an object named mean_cor. I print the output so that I can display the full correlation test output and reuse the correlation value and p value dynamically in my written interpretation
```{r analysis}
mean_cor <- cor.test(week8_tbl$mean_q1q6, week8_tbl$mean_q8q10)
mean_cor
```

I observed a correlation of `r sub("^0\\.", ".", sprintf("%.2f", mean_cor$estimate))` between mean scores on Q1-Q6 and mean scores on Q8-Q10. The associated p-value is `r sub("^0\\.", ".", sprintf("%.2f", mean_cor$p.value))`, which means this correlation is not statistically significant because the p-value is greater than .05. Therefore, I would fail to reject the null hypothesis and conclude that there is not enough evidence for a statistically significant linear relationship between mean scores on Q1-Q6 and mean scores on Q8-Q10.

**Data Export**
I choose to keep timeStart, gender, mean_q1q6, and mean_q8q10 that shiny app needs. timeStart is used for filtering participants before July 1, 2017. mean_q1q6 is x axis, mean_q8q10 is y axis, and gender for male, female, and all. I then use saveRDS to just export a skinny version of the full dataset as an .rds file into the shiny app subfolder for later use in the app. I did everything in a single pipe, following the instruction.
```{r data export}
week8_tbl %>%
  select(timeStart, gender, mean_q1q6, mean_q8q10) %>%
  saveRDS(file = "../shiny/shiny_week8/week8_tbl_skinny.rds")
```