---
title: "PSY 8712 Week 8 Project"
author: "Kyrene"
date: "2026-03-22"
output: 
   html_document:
     theme:
        bootswatch: cosmo
        fg: "#0000FF"
        bg: "#FFFFFF"
     toc: true
     toc_float: true
     df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by https://mybinder.org/v2/gh/Kyrene0629/psy8712-week8.git/HEAD.
An interactive web app is available by clicking this link instead.

**Script Settings and Resources**
```{r Script Settings and Resources, echo = T, warning = F, message = F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(kableExtra)
```

**Data Import and Cleaning**
I imported and cleaned the data like how i did last week. Also, I realize the class for qs are already integer, i should double check before i write that. I reverse-coded q5 by just using 6 - q5 because it is on 1-5 likert scale, then 1 -> 5, 2 -> 4, 3 -> 3, 4 -> 2, 5 -> 1.
```{r section 2 data import and cleaning}
week8_tbl <- read.csv("../data/week3.csv") %>%
  mutate(
    timeStart = ymd_hms(timeStart),
    condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control")),
    gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
    q5 = 6 - q5)
```